\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-10-16 stlc-isorec-prod.tex
stlc compilation figure

@@

\begin{lstlisting}
Family STLCIsorec extends STLC.[@\tanc{STLCIsorec-start}@]
[@\hfill\codecomment{STLC extended with iso-recursive types}@]
FInductive ty : Set +=
| ty_var : id -> ty | ty_rec : id -> ty -> ty.

FInductive tm : Set +=
| tm_fold : tm -> tm | tm_unfold : tm -> tm.

FRecursion tysubst on ty[@\hfill\codecomment{Type-level substitution}@]
motive \lambda(_ : ty), id -> ty -> ty.
Case ty_unit  := [@\dadada@].   Case ty_arrow := [@\dadada@].
Case ty_var   := [@\dadada@].   Case ty_rec   := [@\dadada@].
End tysubst.

FInductive hasty : env -> tm -> ty -> Prop +=
| ht_fold : \forall G t \alpha T,
    hasty G t (tysubst T \alpha (ty_rec \alpha T)) ->
    hasty G (tm_fold t) (ty_rec \alpha T)
| ht_unfold : [@\dadada@].

[@\dadada@][@\hfill\codecomment{Other adjustments}@]
End STLCIsorec.[@\tanc{STLCIsorec-end}@]
\end{lstlisting}

@@

\begin{lstlisting}
Family STLCFixIsorec extends STLC[@\tanc{STLCIsorecfix-start}@]
using STLCFix, STLCIsorec.
[@\hfill\ \ \codecomment{STLC extended with fixpoints and iso-recursive types}@]
End STLCFixIsorec.[@\tanc{STLCIsorecfix-end}@]
\end{lstlisting}

@@

\begin{lstlisting}
Family STLCProd extends STLC.[@\tanc{STLCProd-start}@]
[@\hfill\codecomment{STLC extended with products}@]
FInductive ty : Set +=
| ty_prod : ty -> ty -> ty.

FInductive tm : Set +=
| tm_pair : tm -> tm -> tm
| tm_fst : tm -> tm | tm_snd : tm -> tm.

[@\dadada@][@\hfill\codecomment{Other adjustments}@]
End STLCProd.[@\tanc{STLCProd-end}@]
\end{lstlisting}

@@

\begin{lstlisting}
Family STLCProdIsorec extends STLC[@\tanc{STLCIsorecProd-start}@]
using STLCProd, STLCIsorec.
[@\hfill\ \ \codecomment{STLC extended with products and iso-recursive types}@]
FRecursion tysubst on ty
motive \lambda(_ : ty), id -> ty -> ty.
Case ty_prod := [@\dadada@].[@\hfill\codecomment{Substitution on product types}@]
End tysubst.

End STLCProdIsorec.[@\tanc{STLCIsorecProd-end}@]
\end{lstlisting}

>>>>

\newcommand{\innersep}{\vspace{5pt}}

@@

\begin{lstlisting}
Family STLCIsorec extends STLC.[@\tanc{STLCIsorec-start}@]
[@\hfill\codecomment{STLC extended with iso-recursive types}@]
FInductive tm : Set +=
| tm_fold : tm -> tm | tm_unfold : tm -> tm.[@\innersep@]
FRecursion subst on tm motive [@\dadada@]. [@\dadada@] End subst.[@\innersep@]
FInductive ty : Set +=
| ty_var : id -> ty | ty_rec : id -> ty -> ty.[@\innersep@]
FRecursion tysubst on ty[@\hfill\codecomment{Type-level substitution}@]
  motive \lambda(_ : ty), id -> ty -> ty.
Case ty_unit  := [@\dadada@].   Case ty_arrow := [@\dadada@].
Case ty_var   := [@\dadada@].   Case ty_rec   := [@\dadada@].
End tysubst.[@\innersep@]
FInductive hasty : env -> tm -> ty -> Prop +=
| ht_fold : \forall G t \alpha T,
    hasty G t (tysubst T \alpha (ty_rec \alpha T)) ->
    hasty G (tm_fold t) (ty_rec \alpha T)
| ht_unfold : [@\dadada@].[@\innersep@]
[@\dadada@][@\hfill\codecomment{Other adjustments}@][@\innersep@]
End STLCIsorec.[@\tanc{STLCIsorec-end}@]
\end{lstlisting}

@@

\begin{lstlisting}
Family STLCFixIsorec extends STLC[@\tanc{STLCIsorecfix-start}@]
using STLCFix, STLCIsorec.[@\hfill\codecomment{STLC extended}@]
[@\hfill\codecommentend{with fixpoints and iso-recursive types}@]
End STLCFixIsorec.[@\tanc{STLCIsorecfix-end}@]
\end{lstlisting}

@@

\begin{lstlisting}
Family STLCProd extends STLC.[@\tanc{STLCProd-start}@]
[@\hfill\codecomment{STLC extended with products}@]
FInductive tm : Set +=
| tm_pair : tm -> tm -> tm
| tm_fst : tm -> tm | tm_snd : tm -> tm.[@\innersep@]
FRecursion subst on tm motive [@\dadada@]. [@\dadada@] End subst.[@\innersep@]
FInductive ty : Set +=
| ty_prod : ty -> ty -> ty.[@\innersep@]
[@\dadada@][@\hfill\codecomment{Other adjustments}@][@\innersep@]
End STLCProd.[@\tanc{STLCProd-end}@]
\end{lstlisting}

@@

\begin{lstlisting}
Family STLCProdIsorec extends STLC[@\tanc{STLCIsorecProd-start}@]
using STLCProd, STLCIsorec.[@\hfill\codecommentstart{STLC extended}@]
[@\hfill\codecommentend{with products and iso-recursive types}@]
FRecursion tysubst on ty
  motive \lambda(_ : ty), id -> ty -> ty.
Case ty_prod := [@\dadada@].[@\hfill\codecomment{Substitution on product types}@]
End tysubst.[@\innersep@]
End STLCProdIsorec.[@\tanc{STLCIsorecProd-end}@]
\end{lstlisting}
